Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-29 manuscript/manuscript.tex
Rewrite exponential density equation
Replace "below" for "lower than"
Add missing space before equation reference

\textit{Step 3:}
Apply a second-order GLQ to numerically compute the gravitational fields
(Eq.\ref{eq:glq-var-dens}) generated by each tesseroid obtained in the
previous step.
The numerical integration includes the density function and can be applied
without modification to any continuous function.
The sum of these results is the gravitational field of the original tesseroid.

@@

\begin{equation}
    \rho(r') = A e^{- \frac{b}{R_2 - R_1} (r' - R_1)} + C,
    \label{eq:density-exp}
\end{equation}

@@

The $D$-$\delta$ space exploration for the exponential density function
(Fig.~\ref{fig:grid-search}) showed that values of $D$ determined for the linear density
case are equally applicable to the exponential density case.
Furthermore, the difference with respect to the analytical solution only falls below
0.1\% for values of $\delta$ below 0.1.
It follows that the density-based discretization is required to achieve the desired
accuracy level for non-linear density functions.

>>>>

\textit{Step 3:}
Apply a second-order GLQ to numerically compute the gravitational fields
(Eq.~\ref{eq:glq-var-dens}) generated by each tesseroid obtained in the
previous step.
The numerical integration includes the density function and can be applied
without modification to any continuous function.
The sum of these results is the gravitational field of the original tesseroid.

@@

\begin{equation}
    \rho(r') = A e^{- b \frac{r' - R_1}{R_2 - R_1}} + C,
    \label{eq:density-exp}
\end{equation}

@@

The $D$-$\delta$ space exploration for the exponential density function
(Fig.~\ref{fig:grid-search}) showed that values of $D$ determined for the linear density
case are equally applicable to the exponential density case.
Furthermore, the difference with respect to the analytical solution only falls below
0.1\% for values of $\delta$ lower than 0.1.
It follows that the density-based discretization is required to achieve the desired
accuracy level for non-linear density functions.
